    \cvsection{Experience}
\begin{cventries}
  \cventry
    {Freelance Developer}
    {Kube Cuisines}
    {Trivandrum}
    {Jan. 2016 - Jun. 2016}
    {
      \begin{cvitems}
        \item {Worked as Test Engineer for an internal application written in Django, Celery stack.}
        \item {Wrote reporting APIs for AngularJS based client app.}
      \end{cvitems}
    }
  \cventry
    {Full Stack, Open Source Contribution}
    {Bucket List Tracker}
    {Bangalore}
    {May. 2016 - Exp. Jul. 2016}
    {
      \begin{cvitems}
        \item {Wrote RESTful APIs with token based authentication and OAuth 2 with 100\% test coverage.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {NextDrop Smart Water Systems}
    {Bangalore}
    {Jan. 2015 - Nov. 2015}
    {
      \begin{cvitems}
        \item {Played a key role in data modelling and building data analytics dashboards.}
        \item {Geo-located 80\% of customers with Indian addresses with accuracy of more than 60\% and structured address components from a single string.}
        \item {Implemented a new acquisition channel for new customer registration and a new feedback channel using USSD for interacting with non-smart, text based and feature phone devices.}
        \item {Implemented OpenDataKit based data collection for 95\% of collected data and processed for Django, greatly reducing errors and helped in efficient use of manpower.}
        \item {Wrote API endpoints for analytics and reporting dashboards.}
        \item {Wrote test cases for automated testing in various existing projects to help with Continuous Integration.}
      \end{cvitems} 
    }
  \cventry
    {Software Engineer Intern}
    {Karunya University}
    {Coimbatore}
    {Jul. 2013 - Jun. 2014}
    {
      \begin{cvitems}
        \item {Part of a team which developed a web based Network Management System for the University which managed Internet connectivity in campus and residences.}
        \item {Developed configuration generator for various Linux based network services.}
      \end{cvitems}
    }
  \cventry
    {Academic Project}
    {Karunya University}
    {Coimbatore}
    {Dec. 2012 - Apr. 2013}
    {
      \begin{cvitems}
        \item {Developed a Trusted Third Party Audit for Cloud Storage Services which mainly analyzes the problems in current cloud storage, mainly in the area of data integrity using a Third Party Auditor.}
      \end{cvitems}
    }
  \cventry
    {Backend Developer}
    {Visiware Technologies}
    {Chennai}
    {May 2012}
    {
      \begin{cvitems}
        \item {Worked in a team which developed a module called ``\emph{Ultra Laboratory Utensil}'' in C\# for a live Hospital Management software.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
\end{cventries}
